---
title: "Countries according to different polity score threshold"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    code_folding: show
---

After talking with Dr. Kirby, we found that we used the Polity score at 2017 when we select countries. In this html file, I changed the polity score to 2005, to match the timepoint of wave5. Then I thresholded the polity score at three levels, >6, >7, and >8, yielding 43, 41, and 38 countries. The differences could be viewed below under the corresponding categories.


```{r setup, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=T,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```



```{r, include=FALSE}
library(tidyverse)
```


## Read the data and follow the codebook

```{r read_data}
dat <- readRDS("/Users/zhaoyikai/Desktop/Demo_MI_project/wv5.rds")
#dat6 <- readRDS("/Users/zhaoyikai/Desktop/Demo_MI_project/wv6.rds")
polity = readxl::read_xls("polity_2017.xls")

country_code = readxl::read_xlsx("country_code_5.xlsx", col_names = F)
colnames(country_code) = c("code", "country")

```

### Read in the Polity6+ countries

```{r polity6}
polity_6up_2005 = polity %>%
  filter(year == 2005 & democ >=6) %>%
  dplyr::select(country, year, democ)

polity_6up_2017 = polity %>%
  filter(year == 2017 & democ >=6) %>%
  dplyr::select(country, year, democ)

# manually patch west and east Germany here
polity_6up_2005 = rbind(polity_6up_2005, data.frame("country" = c('West Germany', 'East Germany'), "year" = c(2005, 2005), democ = c(8.5, 8.5)
))


country_name_polity = polity_6up_2005$country 
print(country_name_polity)
```

# When we use a polity score of > 6
What are the countries that were in Polity score that were > 6 in 2017 but not in 2005 (meaning have been improved)?

```{r }
setdiff(polity_6up_2017$country, polity_6up_2005$country)
```






### Let's manually match those NA countries... (Including countries which are below 6 points in polity score) to get a full list of countries! 
```{r append5}
append_df_5 = data.frame("code" = c(288, 320, 344, 356, 360, 364, 368, 380, 400, 458, 504, 604, 704, 710, 724, 756, 818, 900, 901),
                         'country' = c('Ghana', 'Guatemala', 'Hong Kong', 'India', 'Indonesia', 
                                       'Iran', 'Iraq', 'Italy', 'Jordan', 'Malaysia', 'Morocco',
                                       'Peru', 'Viet Nam', 'South Africa', 'Spain', 'Switzerland', 'Egypt', 'West Germany', 'East Germany' ))
```


```{r}
country_code_5_complete = rbind(country_code, append_df_5) # combine the two list together
colnames(country_code_5_complete) = c("code", "country")
country_vector_5 <- setNames(country_code_5_complete$country, country_code_5_complete$code)
country_w_wv5_polity6 = intersect(country_name_polity, country_vector_5)

#dat$country = country_vector_5[as.character(dat$V2A)] # country_vector_5 is the look-up table
print(length(unique(country_w_wv5_polity6)))
#table(dat$country)
country_w_wv5_polity6
```


# When we use a polity score of > 7

### Read in the Polity7+ countries

```{r polity7}
polity_7up_2005 = polity %>%
  filter(year == 2005 & democ >=7) %>%
  dplyr::select(country, year, democ)

# manually patch west and east Germany here
polity_7up_2005 = rbind(polity_7up_2005, data.frame("country" = c('West Germany', 'East Germany'), "year" = c(2005, 2005), democ = c(8.5, 8.5)
))


country_name_polity_7 = polity_7up_2005$country 
```




```{r }

country_code_5_complete = rbind(country_code, append_df_5) # combine the two list together
colnames(country_code_5_complete) = c("code", "country")
country_vector_5 <- setNames(country_code_5_complete$country, country_code_5_complete$code)
country_w_wv5_polity7 = intersect(country_name_polity_7, country_vector_5)

#dat$country = country_vector_5[as.character(dat$V2A)] # country_vector_5 is the look up table
print(length(unique(country_w_wv5_polity7)))
country_w_wv5_polity7
```

# When we use a polity score of > 8

### Read in the Polity8+ countries
```{r polity8}
polity_8up_2005 = polity %>%
  filter(year == 2005 & democ >=8) %>%
  dplyr::select(country, year, democ)

# manually patch west and east Germany here
polity_8up_2005 = rbind(polity_8up_2005, data.frame("country" = c('West Germany', 'East Germany'), "year" = c(2005, 2005), democ = c(8.5, 8.5)
))


country_name_polity_8 = polity_8up_2005$country 
```

```{r dependson=country_name_polity_8}

country_code_5_complete = rbind(country_code, append_df_5) # combine the two list together
colnames(country_code_5_complete) = c("code", "country")
country_vector_5 <- setNames(country_code_5_complete$country, country_code_5_complete$code)
country_w_wv5_polity8 = intersect(country_name_polity_8, country_vector_5)

#dat$country = country_vector_5[as.character(dat$V2A)] # country_vector_5 is the look up table
print(length(unique(country_w_wv5_polity8)))
country_w_wv5_polity8
```

# What is missing from polity6up to polity7up?

```{r}
setdiff(country_w_wv5_polity6, country_w_wv5_polity7)
```

# What is missing from polity7up to polity8up?
```{r}
setdiff(country_w_wv5_polity7, country_w_wv5_polity8)

```


