---
title: "MI part markdown"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Countries that got deleted from the list at the first glance
Please let me know if any of these countries is needed so I can add them back

```{r, echo=FALSE}
country_6up = intersect(polity_6up$country,country_vector)
country_6up[c(3, 5, 17, 19, 25,26,27,28, 31)]

```

## Plots of distributions of answers by country
> Mainly to inspect the distribution of nonnormal values (-5, -2, -1)
> Especially, -2: No answer and -1:Dont know are pretty prevalent in some countries.

This is the density plot for the V152 "tax the rich," **Colombia** has ALL of answers as -4 "Not asked." Thus it has been dropped as well. 
After deleting Colombia, **Georgia** has 14.4& of nonnormal values

```{r, echo=FALSE, warning=FALSE, message=FALSE}
g <- ggplot(data_wv5_6up, aes(V152))+
  geom_density(aes(fill=factor(country)), alpha=0.3) + 
  scale_fill_manual(values = getPalette) +
  labs(title="Density plot of V152", 
       subtitle="Government taxes rich to subsidize poor",
       caption="Source: World Value Survey Wave 5",
       x="Agreement level",
       fill="Country")
 
print(g)
print(sort(rowSums(round(prop.table(tst, 1),3)[,1:3]), TRUE))

```

**Bulgaria** and **Georgia** both have more than 20% of -1:"dont know"s; **Japan** has about 20% of -2:"No answer"
```{r, echo=FALSE, warning=FALSE, message=FALSE}
g <- ggplot(data_wv5_6up, aes(V153))+
  geom_density(aes(fill=factor(country)), alpha=0.3) + 
  scale_fill_manual(values = getPalette) +
  labs(title="Density plot of V153", 
       subtitle="Religious authorities interpret laws",
       caption="Source: World Value Survey Wave 5",
       x="Agreement level",
       fill="Country")
print(g)
print(sort(rowSums(round(prop.table(tst, 1),3)[,1:3]), TRUE))

```
V154 seems okay: the highest nonnormal peaks are **Japan** with only 9.8% and **Serbia** with 9.4%
```{r, echo=FALSE, warning=FALSE, message=FALSE}
g <- ggplot(data_wv5_6up, aes(V154))+
  geom_density(aes(fill=factor(country)), alpha=0.3) + 
  scale_fill_manual(values = getPalette) +
  labs(title="Density plot of V154", 
       subtitle="People choose leaders in free elections ",
       caption="Source: World Value Survey Wave 5",
       x="Agreement level",
       fill="Country")
print(g)
print(sort(rowSums(round(prop.table(tst, 1),3)[,1:3]), TRUE))
```
V155 seems okay with **Argentina** 11.1% as nonnormal values and **Japan** 10.9% with nonnormal values
```{r, echo=FALSE, warning=FALSE, message=FALSE}
g <- ggplot(data_wv5_6up, aes(V155))+
  geom_density(aes(fill=factor(country)), alpha=0.3) + 
  scale_fill_manual(values = getPalette) +
  labs(title="Density plot of V155", 
       subtitle="People receive state aid for unemployment",
       caption="Source: World Value Survey Wave 5",
       x="Agreement level",
       fill="Country")
print(g)
print(sort(rowSums(round(prop.table(tst, 1),3)[,1:3]), TRUE))
```
In terms of V156, there are some countries with lots of -1 pr -2s. **Bulgaria** has 18.7%, **Georgia** 18.4%, **Serbia** 16.4% etc...
```{r, echo=FALSE, warning=FALSE, message=FALSE}
g <- ggplot(data_wv5_6up, aes(V156))+
  geom_density(aes(fill=factor(country)), alpha=0.3) + 
  scale_fill_manual(values = getPalette) +
  labs(title="Density plot of V156", 
       subtitle="Army takes over when government is incompetent  ",
       caption="Source: World Value Survey Wave 5",
       x="Agreement level",
       fill="Country")
print(g)
print(sort(rowSums(round(prop.table(tst, 1),3)[,1:3]), TRUE))
```

For V157, **Japan**, **Bulgaria**, **Serbia** have some unnormal values
```{r, echo=FALSE, warning=FALSE, message=FALSE}
g <- ggplot(data_wv5_6up, aes(V157))+
  geom_density(aes(fill=factor(country)), alpha=0.3) + 
  scale_fill_manual(values = getPalette) +
  labs(title="Density plot of V157", 
       subtitle="Civil rights protect liberties from oppression",
       caption="Source: World Value Survey Wave 5",
       x="Agreement level",
       fill="Country")
print(g)
print(sort(rowSums(round(prop.table(tst, 1),3)[,1:3]), TRUE))
```
The V161 seems okay with **Serbia** 9.9% and **Japan** 8.8
```{r, echo=FALSE, warning=FALSE, message=FALSE}
g <- ggplot(data_wv5_6up, aes(V161))+
  geom_density(aes(fill=factor(country)), alpha=0.3) + 
  scale_fill_manual(values = getPalette) +
  labs(title="Density plot of V161", 
       subtitle="Women have same rights as men ",
       caption="Source: World Value Survey Wave 5",
       x="Agreement level",
       fill="Country")
print(g)
print(sort(rowSums(round(prop.table(tst, 1),3)[,1:3]), TRUE))
```


For the purpose of exploratory analysis, I deleted entries with at least one answer being unnormal (<0), in those troublemaking countries: "Georgia", "Japan", "Bulgaria", "Serbia", "Slovenia." The percentage of the normal entries that are left are such percentage:

```{r}
## original size 
d = c()
for (cn in c("Georgia", "Japan", "Bulgaria", "Serbia", "Slovenia")){
  a = data_wv5_6up %>%
    filter(country == cn) %>%
    nrow()
  d = c(d, a)
}

print(paste("The originial size for", c("Georgia", "Japan", "Bulgaria", "Serbia", "Slovenia"), "are:", d))

## filtered size
b = c()
for (cn in c("Georgia", "Japan", "Bulgaria", "Serbia", "Slovenia")){
  a = data_wv5_6up %>%
    filter(country == cn) %>%
    filter(V152>0 & V153>0 & V154>0 & V155 >0 & V156 >0 & V157 >0 & V161>0) %>%
    nrow()
  b = c(b,a)
}

print(paste("After DELETION of nonnormal entries, the size for", c("Georgia", "Japan", "Bulgaria", "Serbia", "Slovenia"), "are:", b))


### The percentage of the normal entries for countries: "Georgia", "Japan", "Bulgaria", "Serbia", "Slovenia"

print(paste("The percentage of the normal entries that are left for", c("Georgia", "Japan", "Bulgaria", "Serbia", "Slovenia"), "are:", b/d))
```

Surprisingly, there are lots of entries which all the answers are negative, for example in **Japan**

```{r}
Japan %>%
  filter(V152 < 0)
```
and **Bulgaria**
```{r}
data_wv5_6up %>%
  filter(country == "Bulgaria") %>%
  filter(V152 <0)
```


The troublemakers are mainly Japan, Bulgaria, Serbia, Georgia Slovenia etc... which are mostly eastern Europe or Asia countries. They usually have above 10% of nonnormal values in at least one of the items. 

The main issue we need to deal with are those -2 and -1's. Because there are many entries that are populated with not only one negaties, I think we might want to delete them at all.





rmarkdown::render("Explore_nonnormal_values.Rmd")
